PANCHANGE_data_preprocessing

### 2020-07-22 PANCHANGE_data_preprocessing2020-07-15.Rmd
Reviewed COVID algorithm

```{r eval=FALSE, include=FALSE}
# Recode Gender to be binary for the model in RAMP
dat.respirotry.ramp <- dat.respirtaory.ramp %>%
		  mutate(
		    gender_binary_ramp =
		      case_when(
		        Gender == "Male" ~ "Male",
		        Gender == "Female" ~ "Female",
		        Gender == !("Male" | "Female") ~ NA_real_
		      )
		  )
```

++KT: Need help identifying cut offs for COVID probability
```{r eval=FALSE, include=FALSE}
## COVID prediction model for COPING

## Formula to calculate probability 
dat.respirotry.coping <- dat.respirtaory.coping %>%
		  mutate(
		    covid_probability = 
		      (-1.32) - 
		      (0.01*Age) + 
		      (0.44*Sex) + #we have sex here in COPING - use binary Gender variable in RAMP
		      (1.75*anosmia) + #will be renamed
		      (0.31*pcough) +  #will be renamed
		      (0.49*sfatigue) +  #will be renamed
		      (0.39*smeals) #will be renamed
		         )

## Calcualte the odds ratios 
dat.respirotry.coping <- dat.respirtaory.coping %>%
		  mutate(
		    covid_odds_ratio = 
		      exp(covid_probability) / (1 + exp(covid_probability)
		                              )

## label the variable
covid_odds_ratio <- "COVID-19 probability" #IGNORE NEED TO EDIT TO LABEL THE ABOVE VARIABLE

## generate variable covid_odds_ratio_50 -> 0, 0,5 and 1 = 0, 1, 2 (that's a column). Previous code: egen covid_odds_ratio_50 = cut(covid_odds_ratio), at(0,0.5,1) icode
dat.respirotry.coping <- dat.respirtaory.coping %>%
		  mutate(
		    covid_odds_ratio_50_numeric = 
		      case_when(
		        covid_odds_ratio >= 0 & covid_odds_ratio <= 0.4 ~ "0", #I don't know how to categorise these - how does the previous function know when to cut?
		        covid_odds_ratio >= 0.4 & covid_odds_ratio <= 0.6 ~ "1",
		        covid_odds_ratio >= 0.7 & covid_odds_ratio <= 1 ~ "2"
		      )

#create factor with labels
dat.respirotry.coping <- dat.respirtaory.coping %>%
  mutate(
    covid_odds_ratio_50 =
      recode_factor(
        covid_odds_ratio_50_numeric,
        "0" = "No COVID",
        "1" = "Probable COVID",
        "2" = "COVID case"
      )
  )

@@

descr(x = dat.respirotry.coping[,covid_variables],
      round.digits = 2,
      transpose = TRUE)

## create a new label for the variable (50%)
covid_odds_ratio_50 <- "COVID-19 probability >= 50%" #Need to rename variable properly

## looking at the created variable
table(dat.respirotry.coping$covid_odds_ratio_50) #same as before - not sure why this is needed? 
```

>>>>

The below chunk needs to be re-thought - not as simple as categorising gender. 
```{r eval=FALSE, include=FALSE}
# Recode Gender to be binary for the model in RAMP
dat.respiratory.ramp <- dat.respiratory.ramp %>%
		  mutate(
		    gender_binary_ramp =
		      case_when(
		        Gender == "Male" ~ "Male",
		        Gender == "Female" ~ "Female",
		        Gender == !("Male" | "Female") ~ NA_real_
		      )
		  )
```

++KT: Needs to be developed further for RAMP dataset
```{r eval=FALSE, include=FALSE}
## COVID prediction model for COPING

## Formula to calculate probability 
dat.respiratory.coping <- dat.respiratory.coping %>%
		  mutate(
		    covid_probability = 
		      (-1.32) - 
		      (0.01*Age) + 
		      (0.44*Sex) + #we have sex here in COPING - use binary Gender variable in RAMP
		      (1.75*anosmia) + #will be renamed
		      (0.31*pcough) +  #will be renamed
		      (0.49*sfatigue) +  #will be renamed
		      (0.39*smeals) #will be renamed
		         )

## Calcualte the odds ratios 
dat.respiratory.coping <- dat.respiratory.coping %>%
		  mutate(
		    covid_odds_ratio = 
		      exp(covid_probability) / (1 + exp(covid_probability)
		                              )

## generate variable covid_odds_ratio_50 -> 0, 0,5 and 1 = 0, 1, 2 (that's a column). Previous code: egen covid_odds_ratio_50 = cut(covid_odds_ratio), at(0,0.5,1) icode
dat.respiratory.coping <- dat.respiratory.coping %>%
		  mutate(
		    covid_odds_ratio_50_numeric = 
		      case_when(
		        covid_odds_ratio >= 0 & covid_odds_ratio < 0.5 ~ "0", #cut off at 0.5 
		        covid_odds_ratio >= 0.5 & covid_odds_ratio <= 1 ~ "1"
		      )

#create factor with labels
dat.respiratory.coping <- dat.respiratory.coping %>%
  mutate(
    covid_odds_ratio_50 =
      recode_factor(
        covid_odds_ratio_50_numeric,
        "0" = "No COVID",
        "1" = "Probable COVID"
      )
  )

@@

descr(x = dat.respiratory.coping[,covid_variables],
      round.digits = 2,
      transpose = TRUE)

## looking at cases over 0.5
table(dat.respiratory.coping$covid_odds_ratio_50) 
```
